
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliografia}

\bibitem[Ben-Ari06]{benari} Mordechai Ben-Ari, \textit{Principles of Concurrent and Distributed Programming,
  Second Edition}, Addison-Wesley, 2006.

\bibitem[ParProg03]{parprog} Cameron Hughes, Tracey Hughes, \textit{Parallel \& Distributed Programming using C++},
  Adison-Wesley, 2003.

\bibitem[TemG02]{temguide} David Vandevoorde, Nicolai M. Josuttis, \textit{C++ Templates: The Complete Guide},
  Addison Wesley, 2002.

\bibitem[BerLand06]{berland} Krste Asanovi­c, Rastislav Bodik, Bryan Catanzaro, Joseph Gebis,
  Parry Husbands, Kurt Keutzer, David Patterson,
  William Plishker, John Shalf, Samuel Williams, and Katherine Yelick,
  \textit{The Landscape of Parallel Computing Resarch: A view from Berkley},
  Electrical Engineering and Computer Science, University of California at Berkeley, 2006,
  Technical Report No. UCB/EECS-2006-183,
  \url{http://www.eecs.berkeley.edu/Pubs/TechRpts/2006/EECS-2006-183.html}.

\bibitem[ParHist94]{parhist} Wilson, Gregory V Virginia, \textit{The History of the Development of Parallel Computing}, Tech/Norfolk State University, Interactive Learning with a Digital Library in Computer Science, 1994.

\bibitem[Barney]{barney} Blaise Barney, Lawrence Livermore National Laboratory, \textit{Introduction to Parallel Computing}, Livermore Computing, \url{https://computing.llnl.gov/tutorials/tutorials/parallel\_comp/}.

\bibitem[Foster95]{foster} Ian Foster, \textit{Designing and Building Parallel Programs}, Addison-Wesley, 1995.

\bibitem[GenSem00]{gensem} John A. Trono,	William E. Taylor, \textit{Further comments on "A Correct and Unrestrictive Implementation of General Semaphores"}, ACM SIGOPS Operating Systems Review, Volume 34 Issue 3, July 2000.

\bibitem[HasRef]{parhas} \textit{The Glorious Glasgow Haskell Compilation System User's Guide, Version 6.6}, \url{http://www.haskell.org/ghc/docs/6.6/html/users\_guide/index.html}.

\bibitem[Proto]{proto} Eric Niebler, Boost.Proto Library \url{http://www.boost.org/doc/libs/release/libs/proto/index.html}.

\bibitem[BoostThread]{boostthread} Anthony Williams, Boost.Thread Library \url{http://www.boost.org/doc/libs/release/libs/thread/index.html}.

\bibitem[Idioms]{idioms} Sumant Tambe (as the initiator and the lead contributor) and many other authors, \textit{More C++ Idioms}, Wikibooks, \url{http://en.wikibooks.org/wiki/More\_C\%2B\%2B\_Idioms}.

\bibitem[ExpTem03]{exptem} Klaus Kreft, Angelika Langer, \textit{An Introduction to the Principles of Expression Templates}, C/C++ Users Journal, March 2003, \url{http://www.angelikalanger.com/Articles/Cuj/ExpressionTemplates/ExpressionTemplates.htm}.

\bibitem[DisSys02]{dissys} Andrew Tanenbaum, Marteen van Steen, \textit{Distributed Systems}, Prentice Hall, 2002.

\bibitem[SmtPool]{smartpool} Ami Bar, \textit{Smart Thread Pool}, \url{http://www.codeproject.com/KB/threads/smartthreadpool.aspx}.

\bibitem[ThdPool]{threadpool} Brian Goetz, \textit{Thread pools and work queues}, \url{http://www.ibm.com/developerworks/java/library/j-jtp0730/index.html}.

\bibitem[UseCpp96]{usecpp} Gregory V. Wilson, Paul Lu, \textit{Parallel Programming Using C++ Scientific and Engineering Computation}, MIT Press, 1996.

\bibitem[Oracle10]{oracle} \textit{Developing Parallel Programs ? A Discussion of Popular Models}, Oracle White Paper September 2010, \url{http://www.oracle.com/technetwork/server-storage/solarisstudio/documentation/oss-parallel-programs-170709.pdf}

\bibitem[OpenMP09]{openmp} Ruud van der Pas - Sun Microsystems, \textit{An Overview of OpenMP}, 2009, \url{http://openmp.org/mp-documents/ntu-vanderpas.pdf}.

\bibitem[CppLang04]{c++lang} Bjarne Stroustrup, \textit{Jêzyk C++}, WNT, 2004.

\bibitem[TuringCom]{turingcom} Todd L. Veldhuizen, \textit{C++ Templates are Turing Complete}, Indiana University Computer Science.

\end{thebibliography}